Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
Keeping abstract simple

\begin{abstract}
  In the online Graph RePartitioning problem,
  a sequence of communication requests arrives online,
  between pairs of $n$ nodes that are partitioned into $\ell$ clusters
  each of size $k$ (i.e., $n = \ell \cdot k$).
  The objective is to serve these requests while paying a cost that is reasonably close to the optimal cost of serving them given  the whole sequence in advance. 
  This is achieved by opting a sequence of  partitions (a.k.a.~configurations)
  such that frequently communicating nodes (from different clusters)
  are relocated to the same cluster before they inflict too much communication cost.
  A \emph{reconfiguration} (i.e., re-partitioning) is performed by
  moving (i.e., migrating) nodes between clusters at a cost.
  The goal is to jointly minimize communication and migration costs while serving the sequence.

	The best known deterministic algorithm known so far is $O(k^2\cdot \ell^2)$-competitive \cite{repartition-disc},
	and the best known lower bound for the competitive ratio of
	deterministic algorithms is $\Omega(k)$,
 by the reduction from online paging.
	  In this paper, we provide the lower bound of $\Omega(k\cdot \ell)$.
    We also present an optimal algorithm for the case of $k=3$.
  Finally,
  we provide a $O(k\cdot \ell)$-competitive algorithm for the variant
  where the optimal configuration is always a fixed partition
  that incurs zero communication cost through the whole request sequence.
\end{abstract}

@@

>>>>

\begin{abstract}
  In the online Graph RePartitioning problem, we are given a sequence of pairwise communication requests between n nodes, revealed online.
  The objective is to service these requests by partitioning the nodes into $\ell$ clusters, each of size $k$, such that frequently communicating nodes are located in the same cluster.
  The partitioning can be updated by migrating nodes between clusters for a fixed cost.
  The goal is to jointly minimize the amount of inter-cluster communication and migration cost.

	The best known deterministic algorithm known so far was $O(k^2\cdot \ell^2)$-competitive \cite{repartition-disc},
	and the best known lower bound for the competitive ratio of
	deterministic algorithms was $\Omega(k)$,
 by reduction from online paging.
	  In this paper, we provide the lower bound of $\Omega(k\cdot \ell)$.
    We also present an optimal algorithm for the case of $k=3$.
  Finally,
  we provide a $O(k\cdot \ell)$-competitive algorithm for the variant
  where the optimal configuration is always a fixed partition
  that incurs zero communication cost through the whole request sequence.
\end{abstract}

@@

This is achieved by opting a sequence of  partitions (a.k.a.~configurations)
such that frequently communicating nodes (from different clusters)
are relocated to the same cluster before they inflict too much communication cost.
A \emph{reconfiguration} (i.e., re-partitioning) is performed by
moving (i.e., migrating) nodes between clusters at a cost.
The goal is to jointly minimize communication and migration costs while serving the sequence.
